### 2023-06-14 manuscript/chapters/2_neural_fields.qmd
messy compile to PDF

![(TODO remove overlap, change notation, color for activity) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=1_h0=0_phi=sigmoid.mp4){width=400px #fig-p1}

@@

![(TODO remove overlap, change notation, scatter only) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=2_h0=0.mp4){width=500px #fig-p2}

@@

![A cycling neural field with $\delta=6$ and initial condition $h(z_1, z_2, t < 0) = z_1$. The latent trajectory is also computed, and demonstrates the oscillatory behaviour.](figures/embedding_d=2_h0=0_cycling_delta=6.mp4){#fig-cycling-anim}

>>>>

::: {.content-visible when-format="html"}
![(TODO remove overlap, change notation, color for activity) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=1_h0=0_phi=sigmoid.mp4){width=400px #fig-p1}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF remove overlap, change notation, color for activity) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/lol7.jpg){width=400px #fig-p1}
:::

@@

::: {.content-visible when-format="html"}
![(TODO remove overlap, change notation, scatter only) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=2_h0=0.mp4){width=500px #fig-p2}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF remove overlap, change notation, scatter only) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/lol7.jpg){width=500px #fig-p2}
:::

@@

::: {.content-visible when-format="html"}
![A cycling neural field with $\delta=6$ and initial condition $h(z_1, z_2, t < 0) = z_1$. The latent trajectory is also computed, and demonstrates the oscillatory behaviour.](figures/embedding_d=2_h0=0_cycling_delta=6.mp4){#fig-cycling-anim}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF) A cycling neural field with $\delta=6$ and initial condition $h(z_1, z_2, t < 0) = z_1$. The latent trajectory is also computed, and demonstrates the oscillatory behaviour.](figures/lol7.jpg){#fig-cycling-anim}
:::

### 2023-06-14 manuscript/chapters/3_mappings.qmd
messy compile to PDF

$$
\begin{alignat}{2}
S^n : &\{0, \tfrac{1}{2^n}, \cdots, 1-\tfrac{1}{2^n}\}^2 &&\mapsto \{0, \tfrac{1}{4^n}, \cdots, 1-\tfrac{1}{4^n}\} \\
&(v^{(n)}_1,v^{(n)}_2)=(0.b^1_1 b^1_2 \cdots b^1_n, 0.b^2_1 b^2_2 \cdots b^2_n) &&\mapsto \alpha^{(n)}=0.b_1 b_2 \cdots b_{2n}
\end{alignat}
$$ {#eq-Sn}

@@

![(TODO 3D -> 2D only) Equivalence of dynamics, from 3D to 2D.](figures/embedding_3d_2d_1d.mp4)

@@

![Equivalence of dynamics, from 3D to 2D to 1D.](figures/embedding_3d_2d_1d.mp4)

>>>>

$$
\begin{aligned}
S^n : &\{0, \tfrac{1}{2^n}, \cdots, 1-\tfrac{1}{2^n}\}^2 \mapsto \{0, \tfrac{1}{4^n}, \cdots, 1-\tfrac{1}{4^n}\} \\
&(v^{(n)}_1,v^{(n)}_2)=(0.b^1_1 b^1_2 \cdots b^1_n, 0.b^2_1 b^2_2 \cdots b^2_n) \mapsto \alpha^{(n)}=0.b_1 b_2 \cdots b_{2n}
\end{aligned}
$$ {#eq-Sn}

@@

::: {.content-visible when-format="html"}
![(TODO 3D -> 2D only) Equivalence of dynamics, from 3D to 2D.](figures/embedding_3d_2d_1d.mp4)
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF, 3D -> 2D only) Equivalence of dynamics, from 3D to 2D.](figures/lol7.jpg)
:::

@@

::: {.content-visible when-format="html"}
![Equivalence of dynamics, from 3D to 2D to 1D.](figures/embedding_3d_2d_1d.mp4)
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF) Equivalence of dynamics, from 3D to 2D to 1D.](figures/lol7.jpg)
:::
